On exponential sums arising from the classical doubling method

### 2025-03-01 paper.tex
Resolving some issues, probably creating new issues

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor}}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

@@

Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$. It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \FieldNorm{2m}{1}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right).$$

As usual, we rewrite this sum as follows
$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
$$-q^{-m} \tau\left(\chi \circ \FieldNorm{2m}{1}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \finiteFieldExtension{2m}^1$ given by $t \mapsto t^{1 - q^m}$. This map is surjective, and its kernel is $\multiplicativegroup{\finiteFieldExtension{m}}$. Define $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$. Replacing the sum over $x \in \finiteFieldExtension{2m}^1$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
\end{align*}
Replacing $z$ with $t^{q^m} z$, this becomes
\begin{align*}
	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
\end{align*}
Since $\chi \circ \FieldNorm{2m}{1} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero. Hence, we may reduce the sum over $z$ to $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$. Using the fact that $\theta'$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,
\begin{align*}
	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
\end{align*}
By the appendix, this equals
\begin{align*}
	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
\end{align*}

To summarize, we have
$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
	where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$

@@

\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$. Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$. Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
	\begin{align*}
		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
	\end{align*}
\end{theorem}
\begin{proof}
	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},$$
	the facts \begin{equation*}
		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},
	\end{equation*}
	and finally from $$\GaussSumScalar{\chi^2}{\fieldCharacter} = -\tau\left(\chi^2, \fieldCharacter\right).$$
\end{proof}
\begin{remark}
	Suppose that $\pi$ is any irreducible representation of $G$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
	\begin{align*}
		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
	\end{align*}
	Thus \begin{align*}
		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
	\end{align*}
\end{remark}

@@

We will need the following two facts:
\begin{enumerate}
	\item For classical groups $G$ (as the ones we consider in this paper), the Lusztig series $\LusztigSeries{G}{s}$ contains at most one irreducible cuspidal representation. \calvin{False for $SL_2$? True for GSP though. Maybe true with connected center?}
    \elad{No assumption on the center}\calvin{what about the two representations of $SL_2$ in anisotropic torus with the $-1$ character?}\elad{Maybe one of them is not cuspidal (has unipotent fixed vectors). See Lusztig's paper Irreducible Representations of Finite Classical Groups page 172}\calvin{I'm pretty sure neither has them. I haven't read this paper but my guess is the problem is that the centralizer of the $s$ in its Lusztig series is not connected: it is a seimdirect product of $\mathbb{G}_m$ and $\mathbb{Z}/2\mathbb{Z}$.}\elad{You are right, I checked Lusztig's paper and he takes $q$ to be a power of $2$ in the cases with disconnected center. I guess we have to switch to the similitude groups (for which Lusztig explains that we have unique cuspidals)}
	\item The Lusztig series $\LusztigSeries{G}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $G$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
\end{enumerate}
Our theorem is equivalent to the following statement.
\begin{proposition}
	Keep the notations as above. Suppose that $P$ is a parabolic subgroup of $G$ with Levi part $L$. Then for any irreducible cuspidal $\sigma \in \LusztigSeries{L}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{P}{G}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
\end{proposition}
\begin{proof}
	The proof is by induction on $\dim \hermitianSpace$.

@@

	Next, suppose that $L = G$ and that $\pi = \sigma$ is an irreducible cuspidal representation. Let us write $$R_{T, \theta} = \sum_{\Pi} c_\Pi \trace \Pi,$$
	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$. For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
	$$c_{\pi} \cdot \dblVirtualGaussSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	Since $\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblGaussSumScalar{\pi}{\chi}$, the result follows.
\end{proof}

>>>>

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor}}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

@@

Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$. It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right).$$

As usual, we rewrite this sum as follows
$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \finiteFieldExtension{2m}^1$ given by $t \mapsto t^{1 - q^m}$. This map is surjective, and its kernel is $\multiplicativegroup{\finiteFieldExtension{m}}$. Define $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$. Replacing the sum over $x \in \finiteFieldExtension{2m}^1$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
\end{align*}
Replacing $z$ with $t^{q^m} z$, this becomes
\begin{align*}
	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
\end{align*}
Since $\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero. Hence, we may reduce the sum over $z$ to $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$. Using the fact that $\theta'$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,
\begin{align*}
	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
\end{align*}
By the appendix, this equals
\begin{align*}
	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
\end{align*}

To summarize, we have
$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
	where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$

@@

\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$. Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$. Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
	\begin{align*}
		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
	\end{align*}
\end{theorem}
\begin{proof}
	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor},$$
	the facts \begin{equation*}
		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor},
	\end{equation*}
	and finally from $$\GaussSumScalar{\chi^2}{\fieldCharacter} = -\tau\left(\chi^2, \fieldCharacter\right).$$
\end{proof}
\begin{remark}
	Suppose that $\pi$ is any irreducible representation of $G$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
	\begin{align*}
		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
	\end{align*}
	Thus \begin{align*}
		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
	\end{align*}
\end{remark}

@@

We will need the following two facts:
\begin{enumerate}
	\item For the groups $\GroupExtension{G}$ as the ones we consider in this paper, the Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ contains at most one irreducible cuspidal representation.
	\item The restriction of $R_{\GroupExtension{T},\GroupExtension{G}} \left(\GroupExtension{\theta}\right)$ to $G$ is $R_{T, G} \left(\tilde{\theta} \restriction_T\right)$ \cite[Page 140]{DigneMichel2020}. TODO: Write more.
	\item The Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $\GroupExtension{G}$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
\end{enumerate}
Our theorem is equivalent to the following statement.
\begin{proposition}
	Keep the notations as above. Suppose that $P$ is a parabolic subgroup of $G$ with Levi part $L$. Then for any irreducible cuspidal $\sigma \in \LusztigSeries{L}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{P}{G}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
\end{proposition}
\begin{proof}
	The proof is by induction on $\dim_{\quadraticExtension} \hermitianSpace$.

@@

	Next, suppose that $L = G$ and that $\pi = \sigma$ is an irreducible cuspidal representation. Let us write $$R_{T, \theta} = \sum_{\Pi} c_\Pi \trace \Pi,$$
	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$. For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
	$$c_{\pi} \cdot \dblVirtualGaussSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
	Since $\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblGaussSumScalar{\pi}{\chi}$, the result follows.
\end{proof}
